Constraining Black Hole Growth with High-z Quasar Observations

### 2022-09-25 ms.tex
version0925; me integrating all k's revision; except Table2 caption and main text; proximity zone including Masa; and k's 0924 file

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
The early evolution of the quasar luminosity function (QLF) and black hole mass function (BHMF) encodes 
key information on the physics determining the radiative and accretion processes of supermassive 
black holes (SMBHs) in high-redshift quasars.
Although the shape of the QLF has been constrained by recent wide and deep surveys,
it still remains challenging to develop a theoretical model that explains its redshift evolution with BH growth self-consistently.
In this study, based on a semi-analytical model for the formation and growth of seed BHs
in quasar progenitor halos,
we construct the QLF and BHMF of the early BH population that experiences multiple accretion bursts,
in each of which a constant Eddington ratio is assigned following a Schechter distribution function.
Our best-fit model to reproduce the observed QLF and BHMF at $z\simeq 6$
suggests that several episodes of super-Eddington accretion occur
and each of them lasts $\tau \simeq 20-30$ Myr.
The average duty cycle in super-Eddington phases of BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$ is as high as $\simeq 15~\%$,
which is nearly twice that of the entire population.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter-like function
owing to detection limits of quasar surveys.
The predicted redshift evolution of both QLF and BHMF of the earliest BHs suggests a rapid decay of their number and mass
toward higher redshifts of $z>6$, compared to galaxy stellar mass.
This will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
\end{abstract}

@@

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of massive BHs in active galactic nuclei (AGN) is elegantly related to their luminous accretion phases
across the cosmic time \citep{1982MNRAS.200..115S}.
%,1992MNRAS.259..725S}.
The cosmic BH accretion history and their radiative efficiency are well constrained by 
comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
the integration of the QLF based on multi-wavelength observations
\citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T,2022arXiv220607357S}.

Currently the $z\sim 6$ quasar population is well constrained by multiband surveys
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
along with the QLF \citep[e.g.,][]{2015ApJ...798...28K,2016ApJ...833..222J,2017ApJ...847L..15O,2018ApJ...869..150M}.
%and the virial BH mass estimates
%from the \ion{Mg}{2} 2798 $\rm{\AA}$ line width 
%where 
Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
with the Mg~{\sc ii} single-epoch method and bring insights of the mass distribution
(e.g., \citealt{2007AJ....134.1150J,2007ApJ...669...32K};
\citealt{2010AJ....140..546W}, hereafter \citetalias{2010AJ....140..546W};
\citealt{2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}). 
However, extrapolation of the Soltan-Paczy{\'n}ski argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current difficulty of
constructing high-$z$ QLFs \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
Nevertheless, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution and help 
answer questions regarding the existence of SMBHs in the early universe \citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and early development of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.

The shapes of the QLF and BHMF contain key information on the physics characterizing the radiative 
and accretion processes of high-z SMBHs, as well as seeding mechanisms in principle.
Two approaches have been utilized to model those distribution functions.  
The first is semi-analytical modeling, in which BH seed formation, gas accretion, and BH mergers associated 
with the hierarchical growth of the parent dark matter (DM) halos are taken into account in a simplified way. 
This is an effective way of examining the statistical properties of BH populations and making predictions 
that can be directly compared with the observed QLF and BHMF
\citep[e.g.,][]{1998ApJ...503..505H,2010ApJ...718..231S,2018MNRAS.474.1995R,2018MNRAS.481.3278R,
2021MNRAS.508.2706Y,2021ApJ...910L..11K,2022MNRAS.511..616T}. 
However, due to the limitation of capturing the detailed properties of the relevant physics, 
a large number of model parameters need to be calibrated based on the observed distribution functions 
of lower-$z$ quasar populations \citep[e.g.,][]{2007ApJ...669...45H}
and empirical correlations between the SMBH mass and their host galaxy properties seen
in the local universe \citep{2013ARA&A..51..511K}.
The second approach is more phenomenological, using extrapolation of the low-$z$ QLF evolution with 
fitting function forms \citep[e.g.,][]{2019MNRAS.488.1035K,2020MNRAS.495.3252S,2022arXiv220702233F}.
This method also allows us to forecast the higher-$z$ QLF and bring insights for future surveys.
Nevertheless, those semi-analytical and phenomenological approaches introduce numerous physical parameters
and make the key mechanisms reproducing the observed results obscure.
Therefore, it is required to construct a theoretical model that is characterized by a minimum number of parameters
but capable of dealing with the essential physical processes.

To determine the initial conditions of the early BH assembly,
the formation pathway of seed BHs has been extensively investigated by numerical simulations and semi-analytical studies
%Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
%Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
%semi-analytical studies
\citep{2006MNRAS.370..289B,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T,2022arXiv220505717B}.
Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
(i) H$_2$ photo-dissociating irradiation from nearby galaxies
\citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V,2016ApJ...832..134C},
(ii) supersonic baryonic streaming motion that delays gas collapse in halos
\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H,2017MNRAS.471.4878S,2018MNRAS.479.4017I},
and (iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
\citep{2003ApJ...592..645Y,2010Natur.466.1082M,2015ApJ...810...51M,2019Natur.566...85W,2022Natur.607...48L}.
Those effects keep isothermal collapse ($T\sim 8000~{\rm K}$) of massive gas at high accretion rates of $\gtrsim 0.1~\Msunyr$
without vigorous fragmentation \citep{2014MNRAS.445L.109I,2015MNRAS.446.2380B,2016PASA...33...51L},
and allow supermassive stars with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers 
\citep{2013ApJ...778..178H,2013A&A...558A..59S,2019PASA...36...27W,2022arXiv220614459T}.
Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
\citep{2008MNRAS.391.1961D,2009ApJ...695.1430A,2015MNRAS.450.4350I},
recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the heavy-seed formation
can be accelerated in the rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
and the frequency of halo mergers.
As a result, \citet{2021ApJ...917...60L} predicted a top-heavy mass distribution of seed BHs ranging from $10^2-10^5~\Msun$.

In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
% applying the initial mass function (IMF) of seed BHs obtained from \cite{2021ApJ...917...60L}.
applying the semi-analytic seed formation model from \cite{2021ApJ...917...60L} to study the BH growth in the early universe.
We assume that the early BH population experiences multiple accretion bursts, in each of which a constant Eddington ratio is assigned 
following a Schechter distribution function. 
We conduct the Markov Chain Monte Carlo (MCMC) fitting procedure to optimize the BH growth parameters 
so that the observed QLF and BHMF at $z\simeq 6$ are simultaneously reproduced. 
Our best-fit model suggests several episodes of modest super-Eddington accretion and requires
individual burst durations of $\simeq 20-30$ Myr to avoid over(under)-production of BHs at the high-mass end.
Furthermore, we construct the redshift-dependent QLF and BHMF, implying a rapid decay of 
their number and mass toward higher redshifts of $z>6$.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Schechter-like function
owing to detection limits of quasar observations.
Those results will be tested by future deep and wide-field surveys with JWST, RST, and Euclid,
by conducting spectroscopic measurements of individual BH masses and constructing high-$z$ QLFs.

\if0
To construct the picture of BH evolution, the initial mass function (IMF) of BH seeds is required.
Studies have shown that Pop III stars (or the seed BH population) formed in mini-halos is top-heavy, while capped with $\sim 10^3~\Msun$ 
\citep{2014ApJ...781...60H,2015MNRAS.448..568H}.
Focusing on the progenitor halos of supermassive BHs at $z\sim$ 6, 
our recent semi-analytical work produces an IMF of BH seeds ranging from $10^2-10^5~\Msun$ \citep{2021ApJ...917...60L}. 
The IMF is consistent with the three-dimensional radiation hydrodynamical simulations 
constituting the stellar evolution with large scale mass inflow under realistic halo circumstances (Toyouchi et al. 2022).
In this work, we apply the seeding model to examine the BH growth in common regions in the early universe, 
constrained by the observable QLF and BHMF down to $z\sim$ 6, 
% our aim is to understand the growth patterns of early BHs.
\fi

\blue{
This paper is organized as follows. Firstly, in \S~\ref{sec:method} we describe the semi-analytical BH seeding procedure, 
the parameterized BH growth model and how we reproduce the QLF and BHMF dataset at $z\sim$ 6 using these ingredients. 
In \S~\ref{sec:fitting_result} we present the fitting of model parameters constrained by quasar observations.
In \S~\ref{sec:cosm} we discuss the cosmological evolution of BH mass and quasar luminosity functions 
indicated by our best-fit models, as well as the potential detection of these BHs in their early growth.
In \S~\ref{sec:discussion} we present the BH growth tracks and statistical properties along the $z\sim 6$ SMBH growth histories.
We then summarize our findings in \S~\ref{sec:sum} and discuss the potential applications of quasar observations on exploring the high-$z$ universe.
}
Throughout this work, we apply the cosmological parameters from \cite{2016A&A...594A..13P},
i.e., $\Omega_{\mathrm{m}}=0.307,~\Omega_{\Lambda}=0.693,~
\Omega_{\mathrm{b}}=0.0486$, and $H_0=67.7 \mathrm{~km} \mathrm{~s}^{-1} \mathrm{Mpc}^{-1}$.

@@

\vspace{2mm}
\subsection{Seeds}\label{sec:seed}
The QLFs at high redshifts are determined by the BH seeding mechanism and subsequent growth. 
We first describe our model regarding the formation of BH seeds in progenitor DM halos 
that end up in high-$z$ quasar host galaxies with halo mass of $\Mh \gtrsim 10^{11}~\Msun$.
The mass range of those DM halos for $z\sim 6$ quasars is motivated by the halo mass measurement, 
where the rotation velocity of gas based on the [C~{\sc ii}] 158 $\micron$ line width is assumed to be the circular velocity of the halo
%is is motivated by the estimated masses of quasar hosts which are typically up to $\sim 10^{11-13}~\Msun$, 
%probed by the [\ion{C}{2}] 158 $\micron$ fine structure line width 
\citep{2002ApJ...578...90F,2013ApJ...773...44W,2019ApJ...872L..29S}.
Therefore, we consider three parent halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6
and generate $N_{\rm tot} (= 10^4)$ merger trees for each parent halo mass backward in time using the {\tt GALFORM} 
semi-analytic algorithm based on the extended Press-Schechter formalism 
\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}.
%, and study the BH seeds formed therein.
For each tree, we adopt a minimum DM halo mass of $M_{\rm h,min}=10^5~\Msun$, which is small enough to capture 
the earliest star formation episodes via H$_2$ line cooling at the high-$z$ universe \citep{1996ApJ...464..523H,1997ApJ...474....1T}.

We consider seed BH formation in the main progenitors of quasar host galaxies, following a semi-analytical model established by \citet{2021ApJ...917...60L}.
In the highly-biased, overdense regions of the universe, those progenitor halos are likely irradiated by intense H$_2$-photodissociating radiation 
from nearby star-forming galaxies and heat the interior gas by successive mergers. 
The two effects counteracting H$_2$ formation and cooling prevent gas collapse and delay prior star formation \citep[e.g.,][]{2014MNRAS.445..107V,2019Natur.566...85W}.
Under such peculiar circumstances, massive clouds collapse to the halo centers at high accretion rates and leave massive stars (presumably seed BHs) behind.
Our model takes into account various key physical processes on star formation such as halo merger heating, radiative cooling, and
(photo-)chemical reaction networks.
%, and gravitational instability of the central gaseous cores.
The time evolution of the gas dynamics and thermal states is calculated in a self-consistent way with the halo assembly history.
%the gas dynamical and thermal evolution is regulated by the parent halo growth histories, and the environmental streaming velocities.
%
%Next we introduce our seeding model where the gas dynamical and thermal evolution is regulated by the parent halo growth histories, 
%and the environmental streaming velocities.
%In \citet{2021ApJ...917...60L}, we propose an semi-analytical model which 
%traces the gas evolution along its parent halo growth and yields the seed BH mass distribution. 
% The background UV radiation $$ is calculated by semi-analytical arguments of men
%The merger heating and enhancement of background Lyman-Werner radiation intensity $\jlw$ 
%due to halo clustering is taken into account to shape the gas thermal evolution.

In addition, we consider baryonic streaming motion relative to DM produced in the epoch of cosmic recombination at $z_{\rm rec} \simeq 1100$.
%originated from its decoupling with radiation.
This effect also delays gas collapse and star formation in protogalaxies through injection of kinetic energy into gas
\citep[e.g.,][]{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2017Sci...357.1375H,2019MNRAS.484.3510S,2021ApJ...917...60L}.
The amplitude of the streaming velocity is set to $\vbsm = 0$ and $\vbsm=1~\sigma_{\rm bsm}$, where $\sigma_{\rm bsm}=30~{\rm km~s}^{-1} (1+z)/(1+z_{\rm rec})$
is the root-mean-square speed at a redshift of $z$ \citep{2010PhRvD..82h3520T}.
We calculate the effective sound speed of gas as $c_{\rm eff} = \{c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2 \}^{1/2}$ at the center of each progenitor halo,
where $c_{\rm s}$ is the thermal sound speed, $v_{\rm tur}$ is the turbulent velocity of gas (i.e., the specific kinetic energy accumulated through halo mergers), and
the coefficient is set to $\alpha_0=1$\footnote[1]{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
under fast streaming velocities \citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
Note that our previous study in \citet{2021ApJ...917...60L} adopted $\alpha_0=4.7$ \citep{2018ApJ...855...17H}.}.
%
%Besides, the baryonic streaming velocity $\vbsm$ together with the turbulent velocity $v_\mathrm{tur}$ 
%through halo virialization is taken into account
%\footnote{
%We model the effective sound speed of gas as $c_{\rm eff} = \sqrt{ c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2}$,
%where the coefficient $\alpha_0 = 1$ is motivated by previous studies 
%\citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
%}.
When the gas core becomes gravitationally unstable, the evolution of the gas density profile is well described by 
the Penston-Larson self-similar solution \citep{1969MNRAS.144..425P,1969MNRAS.145..271L}. 
The mass accretion rate from the envelope can be written as $\dot{M}=c_{\rm eff}^3/G$,
where $G$ is the gravitational constant.

At the vicinity of an accreting protostar, an accretion disk forms due to angular momentum of the inflowing material from large scales. 
The episodic nature of disk accretion decreases the time-averaged accretion rate onto the protostar as $\Mdot_{\star}=\eta \Mdot$, 
where we adopt $\eta=0.3$ as the conversion efficiency \citep{2016MNRAS.459.1137S, 2022arXiv220614459T}. 
%\blue{
%  (Toyouchi+ find 0.4 actually.)
%}
%Thus, we estimate the accretion rate to estimate the protostellar mass and that of the subsequent seed BH formed. 
The size evolution of an accreting protostar and the radiative feedback strength depend sensitively on whether
the accretion rate becomes higher than a critical value of $\dot{M}_{\mathrm{crit}}=0.04~\Msunyr$ 

>>>>

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
The early evolution of the quasar luminosity function (QLF) and black hole mass function (BHMF) encodes 
key information on the physics determining the radiative and accretion processes of supermassive 
black holes (BHs) in high-redshift quasars.
Although the shape of the QLF has been constrained by recent wide and deep surveys,
it still remains challenging to develop a theoretical model that explains its redshift evolution with BH growth self-consistently.
In this study, based on a semi-analytical model for the formation and growth of seed BHs
in quasar progenitor dark matter halos,
we construct the QLF and BHMF of the early BH population that experiences multiple accretion bursts,
in each of which a constant Eddington ratio is assigned following a Schechter distribution function.
Our best-fit model to reproduce the observed QLF and BHMF at $z\simeq 6$
suggests that several episodes of super-Eddington accretion occur
and each of them lasts $\tau \simeq 20-30$ Myr.
The average duty cycle in super-Eddington phases of BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$ is as high as $\simeq 15~\%$,
which is nearly twice that of the entire population.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Schechter-like function
owing to detection limits of quasar surveys.
The predicted redshift evolution of both QLF and BHMF of the earliest BHs suggests a rapid decay of their number and mass density 
in a cosmic volume toward higher redshifts of $z>6$.
This will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
\end{abstract}

@@

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of massive BHs in active galactic nuclei (AGN) is elegantly related to their luminous accretion phases
across the cosmic time \citep{1982MNRAS.200..115S}.
The cosmic BH accretion history and their radiative efficiency are well constrained by 
comparing the mass density of supermassive BHs (SMBHs) in the local universe and the mass accreted onto BHs inferred from
the integration of the QLF based on multi-wavelength observations
\citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T,2022arXiv220607357S}.

Currently the $z\sim 6$ quasar population is well constrained by multiband surveys
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
along with the QLF \citep[e.g.,][]{2015ApJ...798...28K,2016ApJ...833..222J,2017ApJ...847L..15O,2018ApJ...869..150M}.
Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
with the Mg~{\sc ii} single-epoch method and bring insights of the mass distribution
(e.g., \citealt{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W};
% \citealt{2010AJ....140..546W}, hereafter \citetalias{2010AJ....140..546W};
\citealt{2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}). 
However, extrapolation of the Soltan-Paczy{\'n}ski argument toward higher redshifts of $z\gtrsim$ 6 is still limited 
because of the current capability of high-$z$ quasar observations 
\citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
Nevertheless, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep observations of high-$z$ quasars and their host galaxies will shed light on the early BH evolution and help 
answer questions regarding the existence of SMBHs in the early universe \citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and early development of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.

The shapes of the QLF and BHMF contain key information on the physics characterizing the radiative 
and accretion processes of high-z SMBHs, as well as seeding mechanisms in principle.
Two approaches have been utilized to model those distribution functions.  
The first is semi-analytical modeling, in which BH seed formation, gas accretion, and BH mergers associated 
with the hierarchical growth of the parent dark matter (DM) halos are taken into account in a simplified way. 
This is an effective way of examining the statistical properties of the early BH population and making predictions 
that can be directly compared with the observed QLF and BHMF
\citep[e.g.,][]{1998ApJ...503..505H,2010ApJ...718..231S,2018MNRAS.474.1995R,2018MNRAS.481.3278R,
2021MNRAS.508.2706Y,2021ApJ...910L..11K,2022MNRAS.511..616T}. 
However, due to the limitation of capturing the detailed properties of the relevant physics, 
a large number of model parameters need to be calibrated based on the observed distribution functions 
of lower-$z$ quasar populations \citep[e.g.,][]{2007ApJ...669...45H}
and empirical correlations between the SMBH mass and their host galaxy properties seen
in the local universe \citep{2013ARA&A..51..511K}.
The second approach is more phenomenological, using extrapolation of the low-$z$ QLF evolution with 
fitting function forms \citep[e.g.,][]{2019MNRAS.488.1035K,2020MNRAS.495.3252S,2022arXiv220702233F}.
This method also allows us to forecast the higher-$z$ QLF and bring insights for future surveys.
Nevertheless, those semi-analytical and phenomenological approaches introduce numerous physical parameters
and make the key mechanisms reproducing the observed results obscure.
Therefore, it is required to construct a theoretical model that is characterized by a minimum number of parameters
but capable of dealing with the essential physical processes.

To determine the initial conditions of the early BH assembly,
the formation pathway of seed BHs has been extensively investigated by numerical simulations and semi-analytical studies
\citep{2006MNRAS.370..289B,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T,2022arXiv220505717B}.
Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
(i) H$_2$ photo-dissociating irradiation from nearby galaxies
\citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V,2016ApJ...832..134C},
(ii) supersonic baryonic streaming motion that delays gas collapse in halos
\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H,2017MNRAS.471.4878S,2018MNRAS.479.4017I},
and (iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
\citep{2003ApJ...592..645Y,2010Natur.466.1082M,2015ApJ...810...51M,2019Natur.566...85W,2022Natur.607...48L}.
Those effects keep isothermal collapse ($T\sim 8000~{\rm K}$) of massive gas at high accretion rates of $\gtrsim 0.1~\Msunyr$
without vigorous fragmentation \citep{2014MNRAS.445L.109I,2015MNRAS.446.2380B,2016PASA...33...51L},
and allow supermassive stars with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers 
\citep{2013ApJ...778..178H,2013A&A...558A..59S,2019PASA...36...27W,2022arXiv220614459T}.
Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
\citep{2008MNRAS.391.1961D,2009ApJ...695.1430A,2015MNRAS.450.4350I},
recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the heavy-seed formation
can be accelerated in rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
and frequency of halo mergers.
The mass distribution of seed BHs is expected to be substantially top-heavy, extending the upper mass to $\gtrsim 10^{4-5}~\Msun$
\citep{2021ApJ...917...60L, 2022arXiv220614459T}.
%As a result, \citet{2021ApJ...917...60L} predicted a top-heavy mass distribution of seed BHs ranging from $10^2-10^5~\Msun$.

In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
applying the semi-analytic seed formation model from \cite{2021ApJ...917...60L} to study the BH growth in the early universe.
We assume that the early BH population experiences multiple accretion bursts, in each of which a constant Eddington ratio is assigned 
following a Schechter distribution function. 
We conduct the Markov Chain Monte Carlo (MCMC) fitting procedure to optimize the BH growth parameters 
so that the observed QLF and BHMF at $z\simeq 6$ are simultaneously reproduced. 
Our best-fit model suggests several episodes of modest super-Eddington accretion and requires
individual burst durations of $\simeq 20-30$ Myr to avoid over(under)-production of BHs at the high-mass end.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Schechter-like function
owing to detection limits of quasar observations.
Furthermore, the evolution of the QLF and BHMF implies a rapid decay of 
their number and mass density toward higher redshifts of $z>6$.
Those results will be tested by future deep and wide-field surveys with JWST, RST, and Euclid,
by conducting spectroscopic measurements of individual BH masses and constructing high-$z$ QLFs.

This paper is organized as follows. 
In Section~\ref{sec:method}, we describe the semi-analytical model for BH seeding and subsequent growth via accretion,
and explain the MCMC fitting procedure to constrain the theoretical models by the observations.
%The physical parameters to characterize the QLF and BHMF in the model are optimized with the MCMC fitting to reproduce 
%the observed distribution functions at $z=6$.
In Section~\ref{sec:fitting_result}, we present the fitting results for the model parameters reproducing the observational results,
and discuss the key physics to determining the BH growth.
In Section~\ref{sec:cosm}, we discuss the cosmological evolution of the BHMF and QLF suggested by our best-fit models, 
as well as the detection number of those BHs at $z\sim 6-10$ with Euclid and RST.
In Section~\ref{sec:discussion}, we present the evolutionary tracks of individual BHs and their statistical properties at $z\gtrsim 6$,
based on the growth model calibrated above.
We finally summarize our findings in Section~\ref{sec:sum} and discuss the potential applications of quasar observations on 
exploring the high-$z$ universe.
Throughout this work, we apply the cosmological parameters from \cite{2016A&A...594A..13P},
i.e., $\Omega_{\mathrm{m}}=0.307,~\Omega_{\Lambda}=0.693,~
\Omega_{\mathrm{b}}=0.0486$, and $H_0=67.7 \mathrm{~km} \mathrm{~s}^{-1} \mathrm{Mpc}^{-1}$.

@@

\vspace{2mm}
\subsection{Seed BH formation}\label{sec:seed}
The QLFs at high redshifts are determined by the BH seeding mechanism and subsequent growth. 
We first describe our model regarding the formation of BH seeds in progenitor DM halos 
that end up in high-$z$ quasar host galaxies with halo mass of $\Mh \gtrsim 10^{11}~\Msun$.
The mass range of those DM halos for $z\sim 6$ quasars is motivated by the halo mass measurement, 
where the rotation velocity of gas based on the [C~{\sc ii}] 158 $\micron$ line width is assumed to be the circular velocity of the halo
\citep{2002ApJ...578...90F,2013ApJ...773...44W,2019ApJ...872L..29S}.
Therefore, we consider three parent halos with $\Mh = 10^{11}$, $10^{12}$, and $10^{13} ~\Msun$ at $z=$ 6
and generate $N_{\rm tot} (= 10^4)$ merger trees for each parent halo mass backward in time using the {\tt GALFORM} 
semi-analytic algorithm based on the extended Press-Schechter formalism 
\citep{1974ApJ...187..425P,2000MNRAS.319..168C,2008MNRAS.383..557P}.
For each tree, we adopt a minimum DM halo mass of $M_{\rm h,min}=10^5~\Msun$, which is small enough to capture 
the earliest star formation episodes via H$_2$ line cooling at the high-$z$ universe \citep{1996ApJ...464..523H,1997ApJ...474....1T}.

We consider seed BH formation in the main progenitors of quasar host galaxies, following a semi-analytical model established by \citet{2021ApJ...917...60L}.
In the highly-biased, overdense regions of the universe, those progenitor halos are likely irradiated by intense H$_2$-photodissociating radiation 
from nearby star-forming galaxies and heat the interior gas by successive mergers. 
The two effects counteracting H$_2$ formation and cooling prevent gas collapse and delay prior star formation \citep[e.g.,][]{2014MNRAS.445..107V,2019Natur.566...85W}.
Under such peculiar circumstances, massive clouds collapse to the halo centers at high accretion rates and leave massive stars (presumably seed BHs) behind.
Our model takes into account various key physical processes on star formation such as halo merger heating, radiative cooling, and
(photo-)chemical reaction networks.
The time evolution of the gas dynamics and thermal states is calculated in a self-consistent way with the halo assembly history.

In addition, we consider baryonic streaming motion relative to DM produced in the epoch of cosmic recombination at $z_{\rm rec} \simeq 1100$.
This effect also delays gas collapse and star formation in protogalaxies through injection of kinetic energy into gas
\citep[e.g.,][]{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2017Sci...357.1375H,2019MNRAS.484.3510S,2021ApJ...917...60L}.
The amplitude of the streaming velocity is set to $\vbsm = 0$ and $\vbsm=1~\sigma_{\rm bsm}$, where $\sigma_{\rm bsm}=30~{\rm km~s}^{-1} (1+z)/(1+z_{\rm rec})$
is the root-mean-square speed at a redshift of $z$ \citep{2010PhRvD..82h3520T}.
We calculate the effective sound speed of gas as $c_{\rm eff} = \{c_{\rm s}^2+v_{\rm tur}^2/3+\left(\alpha_0 \vbsm \right)^2 \}^{1/2}$ at the center of each progenitor halo,
where $c_{\rm s}$ is the thermal sound speed, $v_{\rm tur}$ is the turbulent velocity of gas (i.e., the specific kinetic energy accumulated through halo mergers), and
the coefficient is set to $\alpha_0=1$ \footnote[1]{The value of $\alpha_0=1.0$ is motivated by cosmological simulations of massive primordial stars
under fast streaming velocities \citep{2017Sci...357.1375H,2019MNRAS.484.3510S}.
Note that our previous study in \citet{2021ApJ...917...60L} adopted $\alpha_0=4.7$ \citep{2018ApJ...855...17H}.}.
When the gas core becomes gravitationally unstable, the evolution of the gas density profile is well described by 
the Penston-Larson self-similar solution \citep{1969MNRAS.144..425P,1969MNRAS.145..271L}. 
The mass accretion rate from the envelope can be written as $\dot{M}=c_{\rm eff}^3/G$,
where $G$ is the gravitational constant.
